---
title: "MarkdownReport"
author: "Sofiya Tumanova"
date: "2024-01-09"
output: html_document
---

# My first markdown document!

Here you can add some text if you want!

In this case we obtain a result
```{r, eval=T}         # are stating what language we are using (R), and if we want to evaluated it or not (eval = True)
2 + 3                  # when we click 'knit' in R, the code will show in a grey box, and the result will be in a white box below
```
In this case we DO NOT obtain a result    # we don't put the hashtag here because we want this sentence to show up in the document
```{r, eval=F}         
2 + 3                 
```

Using proper packages; the imageRy package has been built in Alma Mater for learning remote sensing
```{r, eval=F}         
library(imageRy)                 
```
Let's import some data, starting with a list of data
```{r, eval=T}         
im.list()                 
```
Importing Mato grosso area image:
```{r, eval=T}         
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```
Importing Mato grosso area image:
```{r, eval=T, warning=F}         
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```
In order to get info on the image, just type the name of the object:
```{r, eval=T}         
mato1992                 
```
Making a new plot of the Mato Grosso area with the NIR ontop of the green component of the RGB space:
```{r, eval=T}         
im.plotRGB(mato1992, r=2, g=1, b=3)                
```
Plotting several images all together:
```{r, eval=T} 
par(mfrow(2,2))
im.plotRGB(mato1992, r=1, g=2, b=3)
im.plotRGB(mato1992, r=1, g=2, b=3) 
im.plotRGB(mato1992, r=1, g=2, b=3) 
im.plotRGB(mato1992, r=1, g=2, b=3) 
```
Calculating spectral indices
```{r, eval=T} 
library(terra)
library(viridisc)
dvi <- mato1992[[1]]-mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(dvi, col=viridisc)
```

Calculating Variability
```{r, eval=T} 
sd3 <- focal(mato1992[[1]], matrix(1/9, 3, 3), fun=sd)
plot(sd3, col = viridisc)

Calculating Variability
```{r, eval=T} 
sd5 <- focal(mato1992[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col = viridisc)
